\bfseries Don't interpolate your data!

### 2022-10-16 main.tex
notes to self

@@

\paragraph{Standard practice}
In standard practice, the individual spectra $y_i$ are interpolated to rest-frame spectra $y'_i$ using an interpolator.
In detail, the data are shifted and also resampled onto the output pixel grid $x_\star$.
The interpolator is a choice; cubic spline, Lanczos, and sinc interpolations are common, since they have good properties with respect to the spectrograph band limit.
Here we choose a cubic spline for convenience ANDY: WHAT SHOULD WE CHOOSE??.

@@

\paragraph{Our method: The forward model}
HOGG: OUR METHOD NEEDS A CONSISTENT NAME USED THROUGHOUT. FORWARD MODEL??

@@

>>>>

HOGG: Something about the LSF being different in different exposures!

@@

\paragraph{Standard Practice (tm)}
In standard practice, the individual spectra $y_i$ are interpolated to rest-frame spectra $y'_i$ using an interpolator.
In detail, the data are shifted and also resampled onto the output pixel grid $x_\star$.
The interpolator is a choice; cubic spline, Lanczos, and sinc interpolations are common, since they have good properties with respect to the spectrograph band limit.
Here we choose a cubic spline for convenience ANDY: WHAT SHOULD WE CHOOSE??.

@@

\paragraph{Our method: Forward Model (tm)}
HOGG: OUR METHOD NEEDS A CONSISTENT NAME USED THROUGHOUT. FORWARD MODEL??

@@

How do you modify to deal with LSF variations (like we have in \textsl{SDSS-V APOGEE}?
